Empirical Evaluation of eval in R

### 2020-08-27 inst/analysis/counts.Rmd

---
title: "Empirical Evaluation of eval in R"
output: html_document
params:
  base_dir: /var/lib/R/project-evalR
editor_options: 
  chunk_output_type: console
---

@@

```{r eval=TRUE}
run_trace_data <- read_fst(PACKAGE_TRACE_RUNS_FILE)
parallel_kaggle_data <- read_fst(KAGGLE_LOG_FILE)

core_data <- read_fst(EVALS_SUM_CORE_FILE)
packages_data <- 
    read_fst(EVALS_SUM_PKGS_FILE) %>%
    mutate(eval_source_type = "package")

# kaggle should be always empty
kaggle_data <- 
    read_fst(EVALS_SUM_KAGGLE_FILE)
    #mutate(eval_source_type == "core")

all_data <- bind_rows(core_data, packages_data, kaggle_data) %>% as_tibble()
all_data <-
    all_data %>%
    mutate(eval_call_srcref = 
          coalesce(eval_call_srcref, 
                   str_c("missing", "::", caller_package, "::", caller_function)))

@@

total_file_count <- length(unique(run_eval_proportion$file))

@@

r("top ten package call count", top_ten_package_call_count)
r("top ten package call perc", ratio(top_ten_package_call_count, total_package_call_count))

r("top ten package site count", top_ten_package_site_count)
r("top ten package site perc", ratio(top_ten_package_site_count, sum(package_calls$site_count)))

@@

```{r callsite-distribution, eval=TRUE}
eval_callsite_table <-
    package_calls %>%
    mutate(site_count = if_else(site_count <= 10, as.character(site_count), 
                        if_else(site_count <= 50, "11--50",
                        if_else(site_count <= 100, "51--100",
                        if_else(site_count <= 150, "101--150",
                        if_else(site_count <= 200, "151--200",
                        if_else(site_count <= 250, "201--250",
                        if_else(site_count <= 300, "251--300",
                        "> 300")))))))) %>%
    group_by(site_count) %>%
    summarize(package_count = n()) %>%
    ungroup() %>%
    arrange(match(site_count, c(1:10,"11--50", "51--100", "101--150", "151--200", "201--250", "251--300", "> 300")))

datatable(eval_callsite_table)

eval_callsite_table %>%
add_column(index = toupper(letters)[1:nrow(eval_callsite_table)]) %>%
pmap_dfr(function(site_count, package_count, index) {
    r(str_c("site summary site count ", index), site_count)
    r(str_c("site summary package count ", index), package_count)
})
```

```{r core-dependent-own-eval}
all_data <- bind_rows(core_data, packages_data, kaggle_data) %>%
  as_tibble() %>%
  mutate(
    package=basename(dirname(dirname(file))),
    core_own_dependent=case_when(
      eval_source == "core"  ~ "core",
      eval_source == "base"  ~ "core",
      package == eval_source ~ "own",
      TRUE ~ "dependent"
    )
  )

# TODO - we need to summarize the data better
# all paths must start with this
stopifnot(nrow(filter(all_data, !startsWith(file, "../../run/"))) == 0)
```

```{r}
cran_programs <- read_fst(CRAN_PROGRAMS_FILE) %>% 
  as_tibble() %>%
  filter(success) %>%
  select(file, corpus)

kaggle_programs <- read_fst(KAGGLE_PROGRAMS_FILE) %>% 
  as_tibble() %>%
  filter(success) %>%
  select(file, corpus)

all_programs <- bind_rows(cran_programs, kaggle_programs)
```

How many programs are missing in the summarized data

```{r}
anti_join(all_programs, all_data, by="file")
```

```{r}
all_programs_cod <-
  map_dfr(
    c("core", "own", "dependent"), 
    ~mutate(
      all_programs,
      core_own_dependent=.,
      nb_ev_calls=0
    )
  )

all_data_summary <- 
  all_data %>%
  select(file, core_own_dependent, corpus, nb_ev_calls) %>%
  right_join(all_programs_cod, by=c("file", "corpus", "core_own_dependent")) %>%
  mutate(nb_ev_calls=ifelse(is.na(nb_ev_calls.x), nb_ev_calls.y, nb_ev_calls.x)) %>%
  select(file, core_own_dependent, corpus, nb_ev_calls)

core_own_dependent <-
  all_data_summary %>%
  group_by(file, core_own_dependent) %>%
  summarize(corpus=first(corpus), eval_calls = sum(nb_ev_calls)) %>%
  ungroup()

# %>%
#   group_by(corpus, core_own_dependent) %>%
#   summarize(
#     total_eval_calls = sum(eval_calls),
#     max_eval_calls = max(eval_calls),
#     min_eval_calls = min(eval_calls),
#     avg_eval_calls = mean(eval_calls)
#   )

vars <- expand.grid(corpus=c("cran", "kaggle"), cod=c("core", "own", "dependent"), stringsAsFactors = FALSE)
map2_dfr(vars$corpus, vars$cod, function(crps, cod) {
  print(filter(core_own_dependent, corpus==crps, core_own_dependent==cod))
  rs(paste(crps, cod, "eval calls"), filter(core_own_dependent, corpus==crps, core_own_dependent==cod)$eval_calls)
}) %>%
  overview_table()

>>>>

---
title: "Empirical Evaluation of eval in R"
output: html_document
params:
  base_dir: ../../../
editor_options: 
  chunk_output_type: console
---

@@

```{r load programs}
cran_programs <- read_fst(CRAN_PROGRAMS_FILE) %>% as_tibble() %>% filter(success)
kaggle_programs <- read_fst(KAGGLE_PROGRAMS_FILE) %>% as_tibble() %>% filter(success)
programs <- bind_rows(
  select(cran_programs, file, corpus),
  select(kaggle_programs, file, corpus)
)
```

```{r eval=TRUE}
core_data <- 
  read_fst(EVALS_SUM_CORE_FILE) %>%
  as_tibble() %>%
  semi_join(programs, by="file")

packages_data <- 
  read_fst(EVALS_SUM_PKGS_FILE) %>%
  as_tibble() %>%
  semi_join(programs, by="file")

# kaggle should be always empty
kaggle_data <- 
  read_fst(EVALS_SUM_KAGGLE_FILE) %>%
  as_tibble() %>%
  semi_join(programs, by="file")

all_data <- 
  bind_rows(core_data, packages_data, kaggle_data)

all_data <-
    all_data %>%
    mutate(eval_call_srcref = 
          coalesce(eval_call_srcref, 
                   str_c("missing", "::", caller_package, "::", caller_function)))

@@

# add the programs that have no evals
run_eval_proportion <-
  bind_rows(
    run_eval_proportion,
    anti_join(programs, run_eval_proportion, by="file") %>% mutate(core=0, package=0, all=0)
  )

total_file_count <- length(unique(run_eval_proportion$file))
stopifnot(total_file_count == nrow(programs))
# anti_join(run_eval_proportion, programs, by="file")

@@

overview_table(
  r("top ten package call count", top_ten_package_call_count),
  r("top ten package call perc", ratio(top_ten_package_call_count, total_package_call_count)),

  r("top ten package site count", top_ten_package_site_count),
  r("top ten package site perc", ratio(top_ten_package_site_count, sum(package_calls$site_count)))
)

@@

```{r callsite-distribution, eval=TRUE}
eval_callsite_table <-
  package_calls %>%
  mutate(
    site_count=cut(
      site_count, 
      breaks=c(0:10, 50, 100, 150, 200, 250, 300, Inf), 
      labels=c(1:10, "11--50", "51--100", "101--150", "151--200", "201--250", "251--300", "> 300"),
      include.lowest = T
    )
  ) %>%
  group_by(site_count) %>%
  summarize(package_count = n())

eval_callsite_table_row <- ceiling(nrow(eval_callsite_table)/3)

eval_callsite_table3 <- map_dfc(seq(1, nrow(eval_callsite_table), eval_callsite_table_row), function(i) {
  x <- tibble(
    eval_callsite_table[i:(i+eval_callsite_table_row), "site_count"],
    eval_callsite_table[i:(i+eval_callsite_table_row), "package_count"]
  )
  colnames(x) <- paste0(colnames(x), i)
  x
})
rownames(eval_callsite_table3) <- NULL

eval_callsite_table3 %>%
  xtable() %>%
  print(
    only.contents=TRUE, 
    include.colnames=FALSE, 
    include.rownames=FALSE,
    hline.after=nrow(eval_callsite_table3),
    file=path(TAGS_DIR, "table-site-package-summary.tex")
  )

datatable(eval_callsite_table3)
```

```{r core-dependent-own-eval}
cod_data <- 
  all_data %>%
  mutate(
    package=basename(dirname(dirname(file))),
    core_own_dependent=case_when(
      eval_source == "core"  ~ "core",
      eval_source == "base"  ~ "core",
      package == eval_source ~ "own",
      TRUE ~ "dependent"
    )
  )
```

```{r}
programs_cod <-
  map_dfr(
    c("core", "own", "dependent"), 
    ~mutate(
      programs,
      core_own_dependent=.,
      nb_ev_calls=0
    )
  )

cod_data_summary <- 
  cod_data %>%
  select(file, core_own_dependent, corpus, nb_ev_calls) %>%
  right_join(programs_cod, by=c("file", "corpus", "core_own_dependent")) %>%
  mutate(nb_ev_calls=ifelse(is.na(nb_ev_calls.x), nb_ev_calls.y, nb_ev_calls.x)) %>%
  select(file, core_own_dependent, corpus, nb_ev_calls)

core_own_dependent <-
  cod_data_summary %>%
  group_by(file, core_own_dependent) %>%
  summarize(corpus=first(corpus), eval_calls = sum(nb_ev_calls)) %>%
  ungroup()

vars <- expand.grid(corpus=c("cran", "kaggle"), cod=c("core", "own", "dependent"), stringsAsFactors = FALSE)
map2_dfr(vars$corpus, vars$cod, function(crps, cod) {
  rs(paste(crps, cod, "eval calls"), filter(core_own_dependent, corpus==crps, core_own_dependent==cod)$eval_calls)
}) %>%
  overview_table()
